A Standard for the Scholarly Citation of Archaeological Data

### 2017-08-26 analysis/paper/paper.Rmd

---
title: "A Standard for the Scholarly Citation of Archaeological Data"
author:
  - "Ben Marwick"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
    fig_caption: yes
    reference_docx: templates/template.docx
bibliography: references.bib
csl: journal-of-archaeological-science.csl
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

@@

Our sample of authors that we wrote email to focused on Journal of Archaeological Science articles on experiments with stone artefacts that were published during 2009 and 2015. We focused on stone artefact experiments because the all research materials in these projects are generated by the researcher, so there are no other stakeholders to consider when determining how to share the data: the researcher has complete control over the data. There are also no risks of damage to people or property in sharing these data because they do not include archaeological sites or human subjects. In contacting the authors, we requested the datasets for use in a graduate seminar with the aim of reproducing the published results and further exploring the data (this stage is still in progress). We promised to contact the authors if we discovered anything new, and not to share the data further without their permission. The data included with this paper is anonymised so the specific authors we contacted are not identifiable.

>>>>

---
title: "A Standard for the Scholarly Citation of Archaeological Data"
author:
  - "Ben Marwick"
  - "Suzanne E. Pilaar Birch"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
    fig_caption: yes
    reference_docx: templates/template.docx
bibliography: references.bib
csl: journal-of-archaeological-science.csl
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

<!-- This is the format for text comments that will be ignored during renderings. Do not put R code in these comments because it will not be ignored.

This document contains code and text supporting the results presented in "A Standard for the Scholarly Citation of Archaeological Data" (draft online at https://docs.google.com/document/d/1UT4RuW4SCkdLGsn2UmNK22vgfJZxljg8ugRstjToCN8/edit).

The source file for this document, and other files in the compendium are online at https://github.com/benmarwick/datacitation
-->

@@

Our sample of authors that we wrote email to focused on Journal of Archaeological Science articles on experiments with stone artefacts that were published during 2009 and 2015. We focused on stone artefact experiments because the all research materials in these projects are generated by the researcher, so there are no other stakeholders to consider when determining how to share the data: the researcher has complete control over the data. There are also no risks of damage to people or property in sharing these data because they do not include archaeological sites or human subjects. In contacting the authors, we requested the datasets for use in a graduate seminar with the aim of reproducing the published results and further exploring the data (this stage is still in progress). We promised to contact the authors if we discovered anything new, and not to share the data further without their permission. The data included with this paper is anonymised so the specific authors we contacted are not identifiable.
>>>>>>> 50d9777774e1d28869879f14da0f740443f2dcc0
